A Computational Account of Default-Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-10-09 paper/paper.tex
even more stuff

Consider an agent faced by choosing the next action
and being guided by rich
reenactment of really happened, hypothetically conceived, and
predicted future events to perfect ongoing behavioral performance.
A particularly attractive computational framework
to describe, quantify, and predict autonomously acting systems like the brain
can be the combination of control theory and reinforcement learning.
It is known that, the more the external world is predictable,
the more mental activity becomes detached from the actual sensory environment
and the more stimulus-independent thoughts occur
(Mason et al., 2007).
These \"offline\" processes may however contribute to optimized control of the organism.
We formalize
a policy matrix to capture the space of possible actions that can be performed
on the environment given the current state. A value matrix 
maps maps expected rewards to environmental objects and events.
Switching between states reduces to a sequential processing model.
In a model-based reinforcement learning approach,
we try to understand the environment always better
starting, at birth, with an environment that is completely unknown.
Informed by outcomes of performed action,
the DMN dynamics are constantly adapted in feed-back loops
that are calibrated by error occurrence.
A DMN framework incorporating reinforcement learning
can naturally embed human behavior
into the tension between exploitative action with immediate gains and
explorative action with longer-term reward schedules.
The implication of the DMN in a diversity of human cognitive processes
can be parsimoneously recast as minimizing prediction error
based on pervasive probabilistic simulations,
thus maximizing reward outcome at various time scales.
Such a purposeful optimization objective
may be solved by a stochastic approximation
based on a brain implementation of Markov Chain Monte Carlo sampling
(Tenenbaum2011Science).
\textit{Control} refers to the influences an agent exterts when interacting
with the environment to encourage preferred states.
Even (necessarily imperfect) memories
of past experience, random mind-wandering and dreams during sleep
may provide meanginful building blocks to iteratively improve
the predictive DMN machinery to optimize the behavior of the organism.

@@

\section{Reinforcement Learning as a computational model for DMN function}
The main idea of this section is to argue that the DMN has biological substrates (gradient
computation, backprop, experience replay, etc.) for all the
major components of an efficient \textit{Reinforcement Learning} algorithm, and all these
components integrate in a plausible way.
Reinforcement Learning (RL) is learning to achieve a goal by interacting with an external
environment. In a general RL framework, an \textit{agent}
interacts with an  environment in a trial-by-error fashion by taking
actions / decisions $a$, which trigger changes in the
\textit{state} of the environment
$s \rightarrow s'$, accompanied by a real-valued \textit{reward}
$r = r(s, a)$ (or regret!, since it can be negative) collected by the
agent. In this view, the environmental is partially controlled by
the action of the agent.
This reward should be thought
of as an instantaneous satisfaction accompanying the execution of
an action.
%% Here the subscript $t$ denotes time, and can be discrete or
%% continuous.
The environment $\mathcal E$ is generally taken as stochastic,
is partially observed, in the sense that only part of the current state is observed by
the agent.
\subsection{Markov Decision Processes}
A popular abstract model for the scenario are so-called \textit{Markov Decision Processes (MDPs)}.
%% In RL, MDPs are the mathematical instantiation of the environment model,
%% which generally can incorporate action probabilities (policy matrix)
%% and/or value function given a state.
%% (Silver: The environment can be fully defined by state space and
%% transition probability matrix.)
is simply a quintuplet $(\mathcal S, \mathcal A, r, \rho, \mu)$ where
\begin{itemize}
\item $\mathcal S$ is the set of states, e.g $\mathcal S = \{\text{happy}, \text{sad}\}$.
\item $\rho : \mathcal S \times \mathcal A \times \mathcal S \rightarrow [0, 1],\; (s,a,s') \mapsto \rho(s'|s,a)$,
  the probability of moving to state $s'$ if action $a$ is taken from state $s$. In addition, one requires that such
  transitions be Markovian. Consequently, the future states are independent of past states and only depend on the present.  
\item $\mathcal A$ is the set of actions, e.g $\mathcal A = \{\text{read}, \text{run},
  \text{laugh}, \text{sympathize}, \text{empathize}\}.$
\item $r : \mathcal S \times \mathcal A \rightarrow \mathbb R$ is the \textit{reward function},
  so that $r(s, a)$ is the instant reward for taking action $a$ in state $s$.
\item $\mu: \mathcal S \rightarrow [0, 1]$ is the prior probability on the states so that
  $\mu(s)$ is the probability that the environment starts-off in state $s$.
\end{itemize}

@@

@@

\subsection{Correspondence between DMN function and RL framework}
\textbf{XXX Put the diagrams and process charts here.}
\begin{itemize}
  \item The policy matrix represents the repertoire of possible actions
  on the world given a current state. It encodes the probabilites of
  choosing actions to be executed in a certain situation.
  \item Given a state, the value function represents the estimated utility of
  being in that state, which is subjective to the agent. 
  For a state $s$, the value function at $s$ namely $V(s)$ define provides a quantitative answer to the question:
  "How desirable is it to be in state $s$ ?"
  For each action $a$ that can be taken from state $s$,
  the Q-value  $Q(s, a)$ defined in \eqref{eq:qval} provides the subjective
  utility of executing a specific action; it answers the question
  "What is the expected utiltiy of taking action $a$ in this situation ?"
  \item The DMN may subserve
  constant exploration of possible future actions and their
  cumulative outcomes. Implicit computation of future choices 
  provides an explanation for purposeful mind-wandering.
  \item hippocampus -> provides perturbed action-transition-state-reward samples
  as a block of "imagined", "hypothesized", "recalled" experience;
  the small variations in these experience blocks allow searching
  a larger space of parameters and possible experiences.
  In the absence of environmental input and feedback
  (e.g., mind-wandering or sleep) pseudo-experiencing possible
  future scenarios and action outcomes.
  Our approach acknowledges the unavoidable stochasticity of
  computation in neuronal processes \cite{faisal2008noise}.
  \item
  \textit{Inference} in the human brain reduces to generalization of
  policy and value adaptations from sampled experiences to
  successful action choices and reward predictions in future states.
  \item In the RL view, plasticity in the DMN arises naturally.
  If an agent behaving optimally in a given environment moves
  to novel, yet unexperienced environments, reward prediction errors will
  massively increase. This will lead to adaptation of the policy matrix
  and value function until the system converges to a
  new steady-state of optimal action decisions given certain states.
  \item The DMN is today known to consistently increase in neural
  activity when engaging cognitive processes that are detached from
  current sensory environment. DMN involvement in thinking about the past,
  the future, and hypothetical possibilities ties in with the
  MDP's implicit computation of action and state cascades as a function
  of what happened in the past.

@@

\section{Relation to other cognitive models}
\subsection{Predictive Coding and Bayesian Brain Hypothesis}
The predictive coding and Bayesian brain framework 
is a frequently evoked idea related to the default mode function
\cite{bar2007}.
According to this view,
cortical responses emerge from continuous functional interaction between
higher and lower levels of the neural processing hierarchy.
This dynamic intercourse enables inference on the world by reconciling
gaps between fresh sensory input and stored prior information. 
Feed-forward sensory experience is constantly calibrated by
top-down modulation at various hierarchical processing levels.
back projections probably outnumber by far the existing input projection in the brain
\cite{salin1995corticocortical}.
It can explains the constructive, generative nature of sensory perception
\cite{friston2010free} and
why motor action is intimately related to sensory expectations
\cite{wolpert1995internal}.
At each stage of neural processing,
an internally generated prediction of the sensory input is
directly compared against the actual input from the environment.
A prediction error at one of the processing levels,
i.e. the difference between sensory input
and internally predicted sensation,
incurs plasticity changes of neuronal back-projections (i.e., model parameters)
for gradually improved future prediction of the environment.
Contextual integration is maintained by top-down modulation of sensorimotor
processing by context-specific a-priori information.
The generative model of how data arise in the
world hence be incorporated into
the current neuronal wiring.
Indeed,
This process permits updates of the internal model of the environment
to best fit the incoming sensory examples.

\begin{itemize}
  \item Both accounts are process theories backed up by plausible
  neurobiological evidence that
  view the brain as a \"statistical organ\"
  generalizing from the past to new experiences.
  \item Both expose a mechanisms of brain plasticity with increased
  adaption of neuronal wiring when faced by unprecedented environmental
  challenges.
  \item The hierarchical aspects from predictive coding
  is re-expressed in MDP in form of
  nested prediction of probable upcoming actions and rewards.
  \item Both model the consequences of action. In RL, the horizon of that
  look into the future is manifest in the $\gamma$ parameter
  in the Bellman equation, but not
  explicitly modeled in the PC account that
  mostly emphasizes prediction about the
  immediate future.
  \item Mismatch negativity of PC is immanent in reward prediction error
  by the difference between actually predicted reward of an action given
  a state and the reward predicted by non-linear regression with graded
  discounting of future rewards.
  \item Sensory experience is a generative process from both views.
  In predictive coding, sensory perception of the external world
  is a generative experience due to modulatory top down experience at
  various hierarchical levels of sensory input processing.
  In our RL view, the (partially observed)
  environmental model is incorporated in the Markov decision
  process, \textit{which can be fully recovered based on the last
  state alone}.
  \item Both provide a parsimoneous explanation why
  humans seem to minimize processing of incoming information
  when the environment is predictable and allocate attention when
  novel stimuli are encountered.
  Similarly, both propose explanations why
  predicting the future is inherently
  linked to information from the past.
\end{itemize}

\subsection{Semantic Hypothesis}
Another frequently proposed account of DMN function revolves
around forming meaning associations and abstract analogies between
the currently experienced environment and
stored knowledge from the past
\cite{bar2007proactive, binder1999conceptual}.
Analogies might naturally tie incoming novel sensory stimuli to
explicit world knowledge stored in past memories
\cite{bar2009proactive}.
Using these semantic analogies to mentally envision scenarios
would improve optimal behavior in the environment
integrated as new memories for future analogical associations.
Such cognitive processes can afford
the internal generation of necessary information
that is not presented in the surrounding environment.
This accounts further explains the reciprocal relationship
between an egocentric first person perspective and
an allocentric bird’s eye perspective immersed in
self-reflection, social knowledge, and autobiographical memories.
%
Closely related to episodic memory, language, problem solving,
planning, others' thoughts, and spatial navigation
as these necessitate abstract world knowledge and abstract assocations
for binding the constituent elements in mental scene construction
\cite{schacter2007remembering}.
These scene generation processes could contribute to interpreting the
present and foretelling the future.
This view is supported by evidence in animals that
could learn a \textit{cognitive map of the environment},
even without reward incentives, and exploit it later
for other means \cite{tolman1948cognitive}.

\begin{itemize}
  \item The notion of semantic or knowledge association is
  incorporated into the MDP as a function of the state and action
  history.
  \item Both: there is no evidence to indicate that predictions of various
  levels of complexity, abstraction, timescale and purpose
  use mechanisms that are qualitatively different. This concurs with
  DMN activity increases across time, space, and content domains
  demonstrated in many neuroimaging studies. The semantic hypothesis
  and RL account provide explanations why hippocampus lesion does
  not only impair retrieving memories, but also hypothetical and future
  thinking \cite{hassabis2007patients}.
  \item The semantic hypothesis and MDP expose mechanisms of
  how alternative decisions could be mentally explored.
  \item While mental scene construction entails a distinction between
  environmental perception and internally generated mind-wandering
  \footnote{``A computational model of how such a process might be structured
  is far from being defined, but it will probably require a form of
  regulation by which perception of the current world is suppressed
  while simulation of possible alternatives are constructed,
  followed by a return to perception of the present.''\cite{buckner2007self}},
  the MDP naturally integrates the former egocentric
  (related to the current action, state and reward) and the later
  allocentric (related to past and future actions, states, and rewards)
  angles on the world in a same optimization problem.
  \item The semantic account of DMN function does not offer 
  a clear explanation how semantic world knowledge and analogies thereof
  lead to prediction about future actions and states.
  \item While both semantic and MDP account propose memory-based internally
  generated information for probabilistic mental models of action outcomes,
  only MDPs render explicit the grounds on which the final action is
  actually chosen (i.e., the estimated cumulative reward).
  \item In sum, the semantic hypothesis lacks an explicit time and
  incentive model.
\end{itemize}

@@

@@

@@

\section{Conclusion}
What single brain function could be most important for existence and survival of the species?
Estimating quantities that depend on how features of an agent’s environment are expected to unfold over the future.
From the perspective of the human condition, it remains unclear what the nature and purpose of a domain-overarching computational mechanism implemented in the high association cortex could be to warriant the high energetic costs.
MDP conceptualize control of the environment.
Obtain reward and avoid pain by adaptive behavior.
How representations of past and future are integrated into
action choice in the present context.
The idealized computational framework explains previous observations about the
DMN in a simple in conception but non-trivially links
together disparate functional hypotheses in the DMN literature.
The default brain function may be reducible to a small number
of well-defined equations.
biological plausibility of dynamic optimization in
optimal substructure
mathematical formalism; statistical solution; adaptive fitness
; formalize and predict; offer statistical control on the brain's default function/operations
stochastic modelling
At the least, we propose an alternative vocabulary to
describe and discuss neuroscientific studies on the DMN.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of RL systems. This makes proposed machine-learning
approach to DMN function not only practically computable but
also neuroscientifically falsifiable.
%
The DMN can be viewed as a smoothing kernel extending
from the relatively recent past to the relatively close future
that constantly estimates complex non-linear gain functions.
-> This is why neuroimaging research revealed activity increases in the DMN
when 
-> This may be why perfect memory has been evolutionarily de-selected,
although it is provably feasible by the neurobiological hardware in humans

>>>>

Consider an agent faced by choosing the next action
and being guided by rich
reenactment of really happened, hypothetically conceived, and
predicted future events to perfect ongoing behavioral performance.
A particularly attractive computational framework
to describe, quantify, and predict autonomously acting systems like the brain
can be the combination of control theory and reinforcement learning.
It is known that, the more the external world is predictable,
the more mental activity becomes detached from the actual sensory environment
\cite{antrobus1966studies, pope1978regulation}.
For instance,
the more the currently executed task is unknown and unpracticed,
the lower the tendency for stimulus-independent thoughts
\cite{filler1973daydreaming, teasdale1995stimulus}.
These \"offline\" processes may however contribute to optimized control of the organism.
We formalize
a policy matrix to capture the space of possible actions that can be performed
on the environment given the current state. A value matrix 
maps maps expected rewards to environmental objects and events.
Switching between states reduces to a sequential processing model.
In a model-based reinforcement learning approach,
we try to understand the environment always better
starting, at birth, with an environment that is completely unknown.
Informed by outcomes of performed action,
the DMN dynamics are constantly adapted in feed-back loops
that are calibrated by error occurrence.
A DMN framework incorporating reinforcement learning
can naturally embed human behavior
into the tension between exploitative action with immediate gains and
explorative action with longer-term reward schedules.
The implication of the DMN in a diversity of human cognitive processes
can be parsimoneously recast as minimizing prediction error
based on pervasive probabilistic simulations,
thus maximizing reward outcome at various time scales.
Such a purposeful optimization objective
may be solved by a stochastic approximation
based on a brain implementation of Markov Chain Monte Carlo sampling
(Tenenbaum2011Science).
\textit{Control} refers to the influences an agent exterts when interacting
with the environment to encourage preferred states.
Even (necessarily imperfect) memories
of past experience, random mind-wandering and dreams during sleep
may provide meanginful building blocks to iteratively improve
the predictive DMN machinery to optimize the behavior of the organism.

@@

\section{Reinforcement Learning as a computational model for DMN function}
The main idea of this section is to argue that the DMN has biological substrates (gradient
computation, backprop, experience replay, etc.) for all the
major components of an efficient \textit{Reinforcement Learning} algorithm, and all these
components integrate in a plausible way.
Reinforcement Learning (RL) is learning to achieve a goal by interacting with an external
environment. In a general RL framework, an \textit{agent}
interacts with an  environment in a trial-by-error fashion by taking
actions / decisions $a$, which trigger changes in the
\textit{state} of the environment
$s \rightarrow s'$, accompanied by a real-valued \textit{reward}
$r = r(s, a)$ (or regret!, since it can be negative) collected by the
agent. In this view, the environmental is partially controlled by
the action of the agent.
This reward should be thought
of as an instantaneous satisfaction accompanying the execution of
an action.
%% Here the subscript $t$ denotes time, and can be discrete or
%% continuous.
The environment $\mathcal E$ is generally taken as stochastic,
is partially observed, in the sense that only part of the current state is observed by
the agent.
\subsection{Markov Decision Processes}
A popular abstract model for the scenario are so-called \textit{Markov Decision Processes (MDPs)}.
Accorind to this model, the environment’s dynamics are fully determined by
its current state.
In RL, MDPs are the mathematical instantiation of the environment model,
which generally can incorporate action probabilities (policy matrix)
and/or value function given a state.
(Silver: The environment can be fully defined by state space and
transition probability matrix.)
is simply a quintuplet $(\mathcal S, \mathcal A, r, \rho, \mu)$ where
\begin{itemize}
\item $\mathcal S$ is the set of states, e.g $\mathcal S = \{\text{happy}, \text{sad}\}$.
\item $\rho : \mathcal S \times \mathcal A \times \mathcal S \rightarrow [0, 1],\; (s,a,s') \mapsto \rho(s'|s,a)$,
  the probability of moving to state $s'$ if action $a$ is taken from state $s$. In addition, one requires that such
  transitions be Markovian. Consequently, the future states are independent of past states and only depend on the present.  
\item $\mathcal A$ is the set of actions, e.g $\mathcal A = \{\text{read}, \text{run},
  \text{laugh}, \text{sympathize}, \text{empathize}\}.$
\item $r : \mathcal S \times \mathcal A \rightarrow \mathbb R$ is the \textit{reward function},
  so that $r(s, a)$ is the instant reward for taking action $a$ in state $s$.
\item $\mu: \mathcal S \rightarrow [0, 1]$ is the prior probability on the states so that
  $\mu(s)$ is the probability that the environment starts-off in state $s$.
\end{itemize}

@@

\paragraph{TODO: Monte Carlo optimization.}
Some text snippets that might be pertinent:
Monte-Carlo simulation can be used to update the agent’s belief state
\cite{silver2010monte}.
Monte-Carlo simulation provides a simple method for evaluating
a state s.
In any MDP, there is at least one optimal policy matrix that
achieves the optimal value function???
The simulator is used to generate sequences of states, observations and rewards. These simulations are used to update the value function, without ever looking inside the black box describing the model’s dynamics. In addition, Monte-Carlo methods have a sample complexity that is determined only by the underlying difficulty of the POMDP, rather than the size of the state space or observation space.
Monte-Carlo simulation can be turned into a simple control algorithm by evaluating all legal actions and selecting the action with highest evaluation [15]. Monte-Carlo simulation can be extended to partially observable MDPs.
In these challenging POMDPs, Monte-Carlo simulation provides an effective mechanism both for tree search and for belief state updates, breaking the curse of dimensionality and allowing much greater scalability than has previously been possible.
Link this to experience sampling in the hippocampus.

@@

\subsection{Correspondence between DMN function and RL framework}
\textbf{XXX Put the diagrams and process charts here.}
\begin{itemize}
  \item The policy matrix represents the repertoire of possible actions
  on the world given a current state. It encodes the probabilites of
  choosing actions to be executed in a certain situation.
  \item Interactions between external and internal sources of
  information are probably commonplace during perception
  \item The MDP frameworks how the human brain could solve
  environmental problems over extended time periods.
  \item Given a state, the value function represents the estimated utility of
  being in that state, which is subjective to the agent. 
  For a state $s$, the value function at $s$ namely $V(s)$ define provides a quantitative answer to the question:
  "How desirable is it to be in state $s$ ?"
  For each action $a$ that can be taken from state $s$,
  the Q-value  $Q(s, a)$ defined in \eqref{eq:qval} provides the subjective
  utility of executing a specific action; it answers the question
  "What is the expected utiltiy of taking action $a$ in this situation ?"
  \item The DMN may subserve
  constant exploration of possible future actions and their
  cumulative outcomes. Implicit computation of future choices 
  provides an explanation for purposeful mind-wandering.
  \item hippocampus -> provides perturbed action-transition-state-reward samples
  as a block of "imagined", "hypothesized", "recalled" experience;
  the small variations in these experience blocks allow searching
  a larger space of parameters and possible experiences.
  In the absence of environmental input and feedback
  (e.g., mind-wandering or sleep) pseudo-experiencing possible
  future scenarios and action outcomes.
  Our approach acknowledges the unavoidable stochasticity of
  computation in neuronal processes \cite{faisal2008noise}.
  \item
  \textit{Inference} in the human brain reduces to generalization of
  policy and value adaptations from sampled experiences to
  successful action choices and reward predictions in future states.
  \item In the RL view, plasticity in the DMN arises naturally.
  If an agent behaving optimally in a given environment moves
  to novel, yet unexperienced environments, reward prediction errors will
  massively increase. This will lead to adaptation of the policy matrix
  and value function until the system converges to a
  new steady-state of optimal action decisions given certain states.
  \item The DMN is today known to consistently increase in neural
  activity when engaging cognitive processes that are detached from
  current sensory environment. DMN involvement in thinking about the past,
  the future, and hypothetical possibilities ties in with the
  MDP's implicit computation of action and state cascades as a function
  of what happened in the past.

@@

\section{Relation to other cognitive models}
\subsection{Predictive Coding Hypothesis}
The predictive coding and Bayesian brain framework 
is a frequently evoked idea related to the default mode function
\cite{bar2007}.
According to this view,
cortical responses emerge from continuous functional interaction between
higher and lower levels of the neural processing hierarchy.
This dynamic intercourse enables inference on the world by reconciling
gaps between fresh sensory input and stored prior information. 
Feed-forward sensory experience is constantly calibrated by
top-down modulation at various hierarchical processing levels.
back projections probably outnumber by far the existing input projection in the brain
\cite{salin1995corticocortical}.
It can explains the constructive, generative nature of sensory perception
\cite{friston2010free} and
why motor action is intimately related to sensory expectations
\cite{wolpert1995internal}.
At each stage of neural processing,
an internally generated prediction of the sensory input is
directly compared against the actual input from the environment.
A prediction error at one of the processing levels,
i.e. the difference between sensory input
and internally predicted sensation,
incurs plasticity changes of neuronal back-projections (i.e., model parameters)
for gradually improved future prediction of the environment.
Contextual integration is maintained by top-down modulation of sensorimotor
processing by context-specific a-priori information.
The generative model of how data arise in the
world hence be incorporated into
the current neuronal wiring.
Indeed,
This process permits updates of the internal model of the environment
to best fit the incoming sensory examples.

\begin{itemize}
  \item Both accounts are process theories backed up by plausible
  neurobiological evidence that
  view the brain as a \"statistical organ\"
  generalizing from the past to new experiences.
  \item Both expose a mechanisms of brain plasticity with increased
  adaption of neuronal wiring when faced by unprecedented environmental
  challenges.
  \item The hierarchical aspects from predictive coding
  is re-expressed in MDP in form of
  nested prediction of probable upcoming actions and rewards.
  \item Both model the consequences of action. In RL, the horizon of that
  look into the future is manifest in the $\gamma$ parameter
  in the Bellman equation, but not
  explicitly modeled in the PC account that
  mostly emphasizes prediction about the
  immediate future.
  \item Mismatch negativity of PC is immanent in reward prediction error
  by the difference between actually predicted reward of an action given
  a state and the reward predicted by non-linear regression with graded
  discounting of future rewards.
  \item Sensory experience is a generative process from both views.
  In predictive coding, sensory perception of the external world
  is a generative experience due to modulatory top down experience at
  various hierarchical levels of sensory input processing.
  In our RL view, the (partially observed)
  environmental model is incorporated in the Markov decision
  process, \textit{which can be fully recovered based on the last
  state alone}.
  \item Adapting the neuronal connections for improved top-down modulation
  takes the concrete form of gradient computation
  \textit{and back-propagation} in MDPs and RL.
  \item Both provide a parsimoneous explanation why
  humans seem to minimize processing of incoming information
  when the environment is predictable and allocate attention when
  novel stimuli are encountered.
  Similarly, both propose explanations why
  predicting the future is inherently
  linked to information from the past.
\end{itemize}

\subsection{Semantic Hypothesis}
Another frequently proposed account of DMN function revolves
around forming meaning associations and analogies between
the currently experience and
abstract knowledge derived from past experiences
\cite{bar2007proactive, binder1999conceptual}.
Analogies might naturally tie incoming novel sensory stimuli to
explicit world knowledge extractable from past memories
\cite{bar2009proactive}.
%
These semantic analogies can be used to mentally envision non-existent scenarios
that would improve optimal behavior in the environment
by simulating future analogical associations.
Such cognitive processes can afford
the internal generation of necessary information
that is not presented in the surrounding environment
by recombining building blocks of
concept knowledge and episodic memories.
Indeed, in aging humans, remembering the past and imaging the future
equally decreased in the level of detail and are associated with
concurrent deficits in forming and integrating relationships between
items \cite{addis2008age, spreng2006temporal}.
A constructive account further explains the reciprocal relationship
between an egocentric first person perspective and
an allocentric bird’s eye perspective immersed in
self-reflection, social knowledge, and autobiographical memories.
%
It is also closely related to episodic memory, language, problem solving,
planning, estimating others' thoughts, and spatial navigation
as these necessitate abstract world knowledge and abstract assocations
for binding the constituent elements in mental scene construction
\cite{schacter2007remembering}.
These scene generation processes could contribute to interpreting the
present and foretelling the future.
This view is for instance supported by evidence in animals that
could learn a \textit{cognitive map of the environment},
even without reward incentives, and exploit it later
for other means \cite{tolman1948cognitive}.

\begin{itemize}
  \item The notion of semantic or knowledge association is
  incorporated into the MDP as the Markov property,
  that is, the current state directly results from the
  agent's history of states and actions. The learned
  value matrix and action transition schedules drive
  stimulus processing and action choice in the present.
  \item In both, semantic hypothesis and MDPs,
  there is no evidence to indicate that predictions of various
  levels of complexity, abstraction, timescale and purpose
  use mechanisms that are qualitatively different. This concurs with
  DMN activity increases across time, space, and content domains
  demonstrated in many neuroimaging studies. The semantic hypothesis
  and RL account provide explanations why hippocampus lesion does
  not only impair retrieving memories, but also hypothetical and future
  thinking \cite{hassabis2007patients}.
  \item Both the semantic hypothesis and MDP expose mechanisms of
  how alternative decision trees could be mentally explored.
  \item While mental scene construction implies a distinction between
  environmental perception and internally generated mind-wandering
  \footnote{``A computational model of how such a process might be structured
  is far from being defined, but it will probably require a form of
  regulation by which perception of the current world is suppressed
  while simulation of possible alternatives are constructed,
  followed by a return to perception of the present.''\cite{buckner2007self}},
  the MDP naturally integrates the former egocentric
  (related to current action, state and reward) and the later
  allocentric (related to past and future actions, states, and rewards)
  angles on the world in a same optimization problem.
  \item The semantic account of DMN function does not offer 
  a mechanistic explanation how semantic world knowledge and analogies thereof
  lead to prediction of future actions and states.
  \item The semantic hypothesis does not explain why memory recall
  for scene construction in humans is fragmentary and noisy
  instead of accurate and reliable.
  Yet, the MDP framework provides an algorithmic explanation in that
  stochasticity of the parameter space search implemented
  by Monte Carlo solvers provably yields better models of the world.
  That is, the purposeful stochasticity of policy and value estimation
  in MDPs provides a candidate explanation for why humans
  have evolved imperfect memories as the better adaptation.
  \item While both semantic and MDP account propose memory-based internally
  generated information for probabilistic mental models of action outcomes,
  only MDPs render explicit the grounds on which the final action is
  actually chosen (i.e., the estimated cumulative reward).
  \item In sum, episodic scene construction according to the semantic
  hypothesis lacks an explicit time and incentive model.
\end{itemize}

@@

The contents of memory and prospection may be nec- essarily and adaptively tied to things social in nature, po- tentially the most behaviorally relevant stimuli. As such, the evolutionary advancement of autonoetic awareness would correspond to the neural processes of theory of mind. The utilization of prospection is arguably of greatest strategic importance, particularly in the secur- ing of mates, protection, and resources (Suddendorf \&

@@

 \begin{itemize}
   \item The sentinel account does not provide a formal mechanisms of
   how attention and memory resources are exactly reallocated when
    encountering a salient environmental stimulus. In contrast,
    the Bellman recursion is weighted at each step by
    $\sum_{a \in A}\pi(a|s)$. This factor weighs which action cascades
    are recursively explorated and which decision trees are neglected,
    which implies allocation of attention and computational load.
 \end{itemize}

@@

\section{Conclusion}
What single brain function could be most important for existence and survival of the species?
Estimating quantities that depend on how features of an agent’s environment are expected to unfold over the future.
From the perspective of the human condition, it remains unclear what the nature and purpose of a domain-overarching computational mechanism implemented in the high association cortex could be to warriant the high energetic costs.
MDP conceptualize control of the environment.
Obtain reward and avoid pain by adaptive behavior.
How representations of past and future are integrated into
action choice in the present context.
The idealized computational framework explains previous observations about the
DMN in a simple in conception but non-trivially links
together disparate functional hypotheses in the DMN literature.
The default brain function may be reducible to a small number
of well-defined equations.
biological plausibility of dynamic optimization in
optimal substructure
mathematical formalism; statistical solution; adaptive fitness
to optimize the organism's fate; contribute to human survival and
creativity.
; formalize and predict; offer statistical control on the brain's default function/operations
stochastic modelling
At the least, we propose an alternative vocabulary to
describe and discuss neuroscientific studies on the DMN.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of RL systems. This makes proposed machine-learning
approach to DMN function not only practically computable but
also neuroscientifically falsifiable.
%
The DMN can be viewed as a smoothing kernel extending
from the relatively recent past to the relatively close future
that constantly estimates complex non-linear gain functions.
-> This is why neuroimaging research revealed activity increases in the DMN
when 
-> This may be why perfect memory has been evolutionarily de-selected,
although it is provably feasible by the neurobiological hardware in humans
